Estimation of flow trajectories in a multi-lines transportation network

### 2023-03-02 latex_files/applied_network_science_article/article_v1.tex
format article
add declarations

\usepackage{caption}

@@

\author[
  addressref={aff1},                   
  corref={aff1},                       
  email={gguex@unil.ch}
]{\inits{G.G.}\fnm{Guillaume} \snm{Guex}}
\author[
  addressref={aff2},
  email={rloup@unil.ch}
]{\inits{R.L.}\fnm{Romain} \snm{Loup}}
\author[
addressref={aff1, aff2},
email={fbavaud@unil.ch}
]{\inits{F.B.}\fnm{François} \snm{Bavaud}}

@@

>>>>

@@

\author[
  addressref={aff1},                                       
  email={gguex@unil.ch}
]{\inits{G.G.}\fnm{Guillaume} \snm{Guex}}
\author[
  addressref={aff2},
  email={rloup@unil.ch}
]{\inits{R.L.}\fnm{Romain} \snm{Loup}}
\author[
addressref={aff1, aff2},
email={fbavaud@unil.ch}
]{\inits{F.B.}\fnm{François} \snm{Bavaud}}

@@

\textbf{\large Declarations}

\section*{Ethical Approval}
Not applicable.

\section*{Authors' contributions}
G.G created the algorithm and participated to the case studies and the manuscript redaction. R.L. participated to the case studies and manuscript redaction, F.B. participated to the manuscript redaction.

\section*{Funding}
No funding was received for this research.

\section*{Availability of data and materials}
All data, codes, and results can be found on the GitHub repository of the project : \url{https://github.com/sliunil/tl_study}.
